Presentation Title

### 2017-07-30 thesis/chapters/ch4-analysis.tex
Edit ch3, 4 and 5

Up to this point we described our system specification in detail.
Of course, specification along does not establish any truths.
In this chapter, we analyse two aspects of our system.
First we show it has the desired properties.
That is, the properties of the consensus protocol and the validation protocol (\Cref{def:consensus} and \Cref{def:validation} respectively) should hold.
Then we analyse the performance, especially the throughput,
and show that it out performs classical blockchain systems.

\section{Correctness in the presense of faults}
Our first objective is to show that \Cref{def:consensus} holds for our consensus protocol.
Then, building on top of it, we show \Cref{def:validation} holds for the validation protocol.
The resulting theorem shows that only using CP blocks in the consensus algorithm implies consensus on TX blocks,
in other words, implicit consensus.

@@

\subsection{Analysis of the consensus protocol}

We begin our analysis by establishing truths on the four properties in \Cref{def:consensus},
namely agreement, validity, fairness and termination.
Using these results, we use mathematical induction to show that they hold for all rounds.

@@

\begin{lemma}
\label{lemma:validity}
For an arbitrary round $r$,
if $\F_r$ is known by all correct nodes and any correct node outputs $\F_{r+1}$,
then (a) $|\C_{r+1}| \ge N - t$ must hold for the $\C_{r+1}$ which was used to create $\F_{r+1}$,
(b) $\F_{r+1}$ must contain at least $n - t$ honest nodes and
(c) $|\F_{r+1}| = n$.
\end{lemma}
\begin{proof}
The validity follows from the validity property of ACS and the definition of our model,
namely $N \ge n + t$ and $n \ge 3t + 1$.
Given $\F_r$, since $N \ge n + t$ , there is at least $n$ nodes that would send their CP block to $\F_r$.
From the validity property of ACS, we know the output must contain the input of at least $n - 2t$ nodes.
But $n -t$ facilitators must have received $N - t$ valid CP blocks, so $|\C_{r+1}| \ge N-t$, this proves (a).
There are $n-t$ honest nodes in $\F_{r+1}$ follows from the model, this proves (b).
Finally, since $N-t \ge (n+t) -t = n$ and $\textsf{get\_facilitators}(\cdot)$ outputs $n$ items, $|\F_{r+1}| = n$ and this proves (c).
\end{proof}

\begin{lemma}
\label{lemma:fairness}
For an arbitrary round $r$,
if $\F_r$ is known by all correct nodes then
every node with a CP block in $\C_{r+1}$, should have an equal probability to be elected as a facilitator in $\F_{r+1}$.
\end{lemma}
\begin{proof}
We have already established that $|\C_{r+1}| \ge N - t \ge n$ from \Cref{lemma:validity}.
Then the proof directly follows from the random oracle model.
Recall that the luck value is computed using $\textsf{H}(\C_{r+1}, || pk_u)$.
Since $pk_u$ is unique for every node that has a CP block in $\C_{r+1}$,
the output of $\textsf{H}(\cdot)$ is uniformly random.
This effectively generates a random permutation
so every node has the same probability of being in the top $n$ for the ordered sequence,
namely the output of $\textsf{get\_facilitators}(\cdot)$.
\end{proof}

\begin{lemma}
\label{lemma:termination}
For an arbitrary round $r$,
if $\F_r$ is known by all correct nodes then
every correct node eventually outputs some $\F_{r + 1}$.
\end{lemma}
\begin{proof}
This follows directly from the properties of the channel (eventual delivery)
and the termination property of ACS.
That is, $\F_r$ eventually receives all the CP blocks required to begin ACS.
ACS eventually terminates.
Finally the results are eventually dissemminated to all the nodes.
\end{proof}

@@

In the base case, agreement, validity fairness and termination follows directly from the bootstrap protocol,
due to the bootstrap oracle.
Note that the result is $\F_1$, which indicates the facilitators that are agreed in round 1, who are responsible for driving the ACS protocol in round 2.

@@

\subsection{Correctness of validation}
The consensus protocol (on CP blocks and facilitators) is the backbone for consensus on transactions.
In this section we build on top of \Cref{theorem:consensus} to show that most (except liveness) properties in \Cref{def:validation} can be satisfied.

\begin{lemma}
% (Correctness of the validation protocol)
The validation protocol outputs the correct result
according to the validity definition.
\end{lemma}
\begin{proof}
The algorithm (\Cref{alg:get-validity}) is the validity definition.
\end{proof}

\begin{theorem}
\label{theorem:validation-agreement}
% (Agreement of the validation protocol)
If any correct node decides on the validity (except when it is \emph{unknown}) of a transaction,
then all other correct nodes are able to reach the same conclusion or \emph{unknown}.
\end{theorem}
\begin{proof}
We proof by contradiction.
Without loss of generality, for some transaction $t$ with an agreed fragment $F$,
node $u$ decides \emph{valid} but node $v$ decides \emph{invalid}.
Then there exist a fragment $F' = \{ \dots, t', c'\}$ which $u$ received that contains a valid pair of $t$---$t'$.
There also exist a fragment $F'' = \{ \dots, t'', c''\}$ which $v$ received that does not contain or contains an invalid pair---$t''$.
In both cases, the $\textsf{get\_validity}(\cdot)$ function must have reached \Cref{line:valid-fragment}.
Due to \Cref{theorem:consensus}, we have $c' = c''$, otherwise the result would be \emph{unknown}.
Since $c' (= c'') = \langle \textsf{H}(t'), \dots \rangle$ we must have $\textsf{H}(t') = \textsf{H}(t'')$ and $t' \ne t''$ (because $t''$ is invalid).
In other words, whoever sent $F''$ must be able to create some $t''$ that has the same digest as $t'$.
But we assumed that the adversary can only perform polynomial-time algorithm,
so in order to find $t''$ it needs to query the random oracle exponentially many times.
Thus we have a contradiction and this completes the proof.
\end{proof}

\Cref{theorem:validation-agreement} is our first major result.
It shows that consensus on CP blocks would lead to consensus on TX blocks when the nodes are running the validation protocol.
Just like in our prior work~\cite{implicitconsensus}, we call this behaviour implicit consensus.
One of the main advantages over running a consensus algorithm on all the transactions is that 
the rate of transaction is no longer dependent on the consensus algorithm---ACS.
This enables horizontal scalability where adding new nodes would lead to higher global transaction rate.
In addition, a convenient consequence \Cref{theorem:validation-agreement} is unforgeability.
That is, no polynomial time adversary is able to create two chains $F = \{ \dots, t, c\}$ $F' = \{ \dots, t', c\}$ with correct hash pointers and the same end of chain $c$.
% Another way to think about it is if a transaction can be forged, then it cannot be agreed.

\subsection{Impossibility of liveness}
While \Cref{theorem:validation-agreement} is a major result that allows significantly improved performance over traditional blockchain systems,
it is not perfect.
Now we show a negative result, where the liveness property of \Cref{def:validation} cannot be attained.
Meaning that trasanctions with adversaries cannot always be validated.

\begin{lemma}
There exist a valid transactions that cannot be validated eventually.
\end{lemma}
\begin{proof}
We proof by providing a counterexample.
Suppose nodes $u$ and $v$ correctly perfomed the TX protocol which resulted a transaction $t$.
Then when $u$ wants to validate $t$, it does so by sending \texttt{vd\_req} message to $v$.
$v$ can act maliciously and ignore all \texttt{vd\_req} message, thus $t$ can never be validated.
\end{proof}
Although this is a negative result, it does not put the adversary in an advantageous position.
If the adversary is observed to ignore validation requests, then the honest nodes may prefer not to transact with her in the future.
Thus, to stay relevant in the system, the adversary need to comply to the protocol.

@@

\section{Performance analysis}
\label{sec:performance-analysis}
This section aims to analytically answer our research question.
That is, does the global throughput increase linearly with respect to the population size?
We begin by looking at the communication and time complexity of the consensus protocol,
and then the bandwidth requirement for a single transaction.
We build on top of those results to analyse do the global throughput analysis.

\subsection{Communication complexity of the consensus protocol}
\label{sec:cons-complexity}
The consensus protocol can bee seen as three parts.
Thus the communication complexity is the sum of these three parts.
The first part is when every node sends their CP block to all the facilitators, which is $O(Nn)$ since there are $N$ nodes and $n$ facilitators.
Or simply $O(N)$ if we consider $n$ as a constant.

The second part is ACS.
The communication complexity of ACS is $O(n^2|v| + \lambda n^3 \log n)$~\cite{miller2016honey},
where $|v|$ is the size of largest message and $\lambda$ is the security parameter.
Note that the security parameter is the same as the one for our random oracle described in \Cref{sec:model-assumptions}.
In particular, it is from the use of $\textsf{H}(\cdot)$ in the reliable broadcast phase in ACS.
In our system, we wish to understand the scalability properties.
Thus we consider the complexity as a function of $N$ rather than $n$ or $\lambda$.
Since $|v|$ is at most all the CP blocks from every node, we have $|v| = cN$,
where $c$ is a constant representing the size of one CP block.
Therefore the communication complexity of ACS in our system is $O(N)$.
Since we use a constant $n$, $O(N)$ communication complexity also holds for a single facilitator.

The third and final part is the dissemination, where the facilitators broadcast the consensus result along with their signatures.
For the same reason as the first part, this is also $O(N)$.
Thus the combined communication complexity when $n$ is a constant is $O(N)$.

@@

\subsection{Duration of the consensus protocol}
\label{sec:cons-duration}
In order to make arguments on bandwidth or throughput, which are concepts that depend on time,
we must make some assumptions regarding our computational model to make arguments on the duration of the consensus protocol.
Note that it is not the same as the time complexity typically used in distributed systems.
In analysis of distributed systems, time complexity is often in terms of the number of rounds.
For example, ACS runs in a constant number of rounds because its subprotocols---reliable broadcast and binary Byzantine consensus---also run in a constant number of rounds.
However, in practice, making a unit of communication always has some overhead associated with it, for example serialising and writing it to some network socket.
Hence, for the remainder of our performance analysis, we add the following to our computational model.
For every unit of communication, we assume they take some non-negligible but constant time to perform.
Hence, from~\Cref{sec:cons-complexity} and the fact that the consensus protocol uses a constant number of rounds,
it follows that the consensus protocol has a duration of $O(N)$.

\subsection{Communication cost for transactions}
\label{sec:communication-cost-for-tx}
With the analysis on the duration of the consensus protocol,
we are ready to analyse the amount of data required to be transmitted over a link per transaction,
which we call the communication cost per transaction.
% First, we define bandwidth as the ``amount of data a link or network path can deliver per unit of
% time''~\cite{prasad2003bandwidth}.
We know that to create and then validate a transaction,
the communication cost per transaction is of $O(l)$,
where $l$ is the length of the agreed fragment.
This can be seen from the fact that the largest message by far is the \texttt{vd\_resp} message,
which contains the agreed fragment.
The other messages (\texttt{tx\_req}, \texttt{tx\_resp} and \texttt{vd\_req}) are constant factors.
If we assume that every node performs transactions at a constant rate of $r_{\text{tx}}$ per second.
Then
$$l = r_{\text{tx}} D_{\text{c}},$$
where $D_{\text{c}}$ is the duration a round of the consensus protocol.
But from \Cref{sec:cons-duration},
we know that $D_{\text{c}}$ is of $O(N)$, thus the communication cost per transaction is $O(N)$.
This is intuitive because round duration would be longer if there are more CP blocks (more $N$), which means that the agreed fragments are longer (assuming nodes transact at a constant rate).
The behaviour is also verified experimentally in \Cref{ch:implementation}.

\subsection{Global throughput}
\label{sec:global-throughput}
Using our results so far, we are able to analyse the global throughput.
First we clarify the bandwidth definition, which is ``the data rate at which a network link or a network path can transfer''~\cite{prasad2003bandwidth}.
Now, suppose every node has some fixed bandwidth per link $C$ and $N$ links.
They also make transactions at $r_{\text{tx}}$ per second.
Then we have the inequality
$$NC \ge r_{\text{tx}} l,$$
where $l$ is the length of the the agree fragment as before.
The inequality suggests that the rate for which transactions and validations are made cannot exceed the total bandwidth of all the links.

We note that the inequality does not hold if the node is only transacting with a small sample of some subset of the population.
This is because it cannot use all the bandwidth available in all the links.
For instance, if the node is only transacting with one other node, then it can only use the bandwidth of one link which is only $C$.
However, if that is the case, we can intelligently cache the \texttt{vd\_resp} messages.
Thus multiple transactions can be validated with a single \texttt{vd\_resp} message.
For this work, we analyse the worst case where every node transacts with a random node from the population,
and a new \texttt{vd\_resp} must be sent for every \texttt{vd\_req} message.

Consider the case where the system is making use of all the bandwidth, i.e. $NC = r_{\text{tx}} l$.
Recall that $l$ is of $O(N)$, that means LHS and RHS both grow linearly with respect to $N$.
Hence, there exist some constant $r_\text{tx}$ that makes use of all the available bandwidth regardless of $N$.
Finally, if every node in the network is transacting at a constant rate, then the global throughput (in terms of transactions per second) is of $O(N)$.
If the system is not making use of all the bandwidth.
We also maintain a constant transaction rate by the same argument.
Thus a global throughput is also $O(N)$.
We verify both of these claims experimentally in~\Cref{sec:evaluation}.

@@

The problem can be formulated as follows.
Suppose an urn contains $N$ balls, $t$ are black and $N-t$ are white.
If $n$ balls are drawn uniformly at random without replacement,
what is the probability that $\lfloor \frac{n-1}{3} \rfloor$ are black?
The random variable $X$ in this case is the number of black balls, or the number of successful events.
It follows the hypergeometric distribution since we pick balls \emph{without} replacement~\cite{skala2013hypergeometric}.
Hence, we are interested in the following probability.
$$
1 - \sum_{k = 0}^{\lfloor \frac{n-1}{3} \rfloor} \Pr[X = k] = 
1 - \sum_{k = 0}^{\lfloor \frac{n-1}{3} \rfloor} \frac{ \binom{t}{k} \binom{N-t}{n-k} }{ \binom{N}{n} }
$$

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=1.0\textwidth]{hypergeometric}
  \caption{Plot of the probability of selecting more than $\lfloor \frac{n-1}{3} \rfloor$ black balls for
  different numbers of }
  \label{fig:hypergeometric}
\end{figure}

On the other hand, due to the fact that hypergeometric distributions have light tails,
that is ``faster-than-exponential fall-off''~\cite{skala2013hypergeometric},
the probability for picking more than $\lfloor \frac{n-1}{3} \rfloor$ black balls when 
the expected value is  much smaller than $\lfloor \frac{n-1}{3} \rfloor$ is small.
We can use tail inequality to bound the probability of picking more than $\lfloor \frac{n-1}{3} \rfloor$ black balls when only $n\alpha$ are black where $0 \le \alpha \le \lfloor \frac{n-1}{3} \rfloor / n$.
The tail inequality is
$$
\Pr[X \ge E[X] + \tau n] \le e^{-2\tau^2n},
$$
where $E[X] = n\alpha$.
We are interested in $\Pr[X \ge \lfloor \frac{n-1}{3} \rfloor + 1]$, so
\begin{align*}
\tau &= \frac{\lfloor \frac{n-1}{3} \rfloor + 1}{n} - \alpha
\end{align*}
Putting $\tau$ back into the tail inequality we get the following bound.
$$
\Pr[X \ge \lfloor \frac{n-1}{3} \rfloor + 1] \le e^{-2 \big(\frac{\lfloor  \frac{n - 1}{3} \rfloor + 1}{n} - \alpha \big)^2 n}
$$

>>>>

Up to this point we described our system specification in detail.
Of course, specification alone does not establish any truths.
In this chapter, we evaluate our system analytically.
First we show it has the desired properties.
That is, the properties of the consensus protocol and the validation protocol (\Cref{def:consensus} and \Cref{def:validation} respectively) should hold.
Then we analyse the performance, especially the throughput,
and show that it out performs classical blockchain systems.
Finally, we consider the case where the $n \ge 3t + 1$ assumption is violated,
and show the effect of it in our system.

\section{Correctness in the presense of faults}
Our first objective is to show that \Cref{def:consensus} holds for our consensus protocol.
Then, building on top of it, we show \Cref{def:validation} holds for the validation protocol.
The resulting theorem shows that only using CP blocks in the consensus algorithm implies consensus on TX blocks.

@@

\subsection{Correctness of the consensus protocol}

We begin our analysis by establishing truths on the four properties in \Cref{def:consensus},
namely agreement, validity, fairness and termination for an arbitrary round.
Using these results, we use mathematical induction to show that they hold for all rounds.

@@

\begin{lemma}
\label{lemma:validity}
For an arbitrary round $r$,
if $\F_r$ is known by all correct nodes and any correct node outputs $\F_{r+1}$,
then (a) $|\C_{r+1}| \ge N - t$ must hold for the $\C_{r+1}$ which was used to create $\F_{r+1}$,
(b) $\F_{r+1}$ must contain at least $n - t$ honest nodes and
(c) $|\F_{r+1}| = n$.
\end{lemma}
\begin{proof}
The validity follows from the validity property of ACS and the definition of our model,
namely $N \ge n + t$ and $n \ge 3t + 1$.
Given $\F_r$, since $N \ge n + t$ , there is at least $n$ nodes that would send their CP block to $\F_r$.
From the validity property of ACS, we know the output must contain the input of at least $n - 2t$ nodes.
But $n -t$ facilitators must have received $N - t$ valid CP blocks, so $|\C_{r+1}| \ge N-t$, this proves (a).
There are at least $n-t$ honest nodes in $\F_{r+1}$ which follows from our assumption, this proves (b).
Finally, since $N-t \ge (n+t) -t = n$ and $\textsf{get\_facilitators}(\cdot)$ outputs $n$ items, $|\F_{r+1}| = n$ and this proves (c).
\end{proof}

\begin{lemma}
\label{lemma:fairness}
For an arbitrary round $r$,
if $\F_r$ is known by all correct nodes then
every node with a CP block in $\C_{r+1}$, should have an equal probability to be elected as a facilitator in $\F_{r+1}$.
\end{lemma}
\begin{proof}
We already established that $|\C_{r+1}| \ge N - t \ge n$ from \Cref{lemma:validity}.
Then the proof directly follows from the random oracle model.
Recall that the luck value is computed using $\textsf{H}(\C_{r+1}, || pk_u)$.
Since $pk_u$ is unique for every node that has a CP block in $\C_{r+1}$,
the output of $\textsf{H}(\cdot)$ is uniformly random.
This effectively generates a random permutation
so every node has the same probability of being in the top $n$ for the ordered sequence,
namely the output of $\textsf{get\_facilitators}(\cdot)$.
\end{proof}

\begin{lemma}
\label{lemma:termination}
For an arbitrary round $r$,
if $\F_r$ is known by all correct nodes then
every correct node eventually outputs some $\F_{r + 1}$.
\end{lemma}
\begin{proof}
This follows directly from the properties of the channel (eventual delivery)
and the termination property of ACS.
That is, $\F_r$ eventually receives all the CP blocks required to begin ACS,
and then ACS eventually terminates.
Finally, the results are eventually dissemminated to all the nodes.
\end{proof}

@@

In the base case ($r = 1$), agreement, validity fairness and termination follows directly from the bootstrap protocol.
Note that the result is $\F_1$, which indicates the facilitators that are agreed in round 1, who are responsible for driving the ACS protocol in round 2.

@@

\subsection{Correctness of the validation protocol}
The consensus protocol (on CP blocks and facilitators) is the backbone for consensus on transactions.
In this section we build on top of \Cref{theorem:consensus} to show that the properties except liveness in \Cref{def:validation} can be satisfied.

\begin{theorem}
\label{theorem:validation-agreement}
% (Agreement of the validation protocol)
The validation protocol satisfies agreement and validity properties.
\end{theorem}
\begin{proof}
We proof the agreement property by contradiction.
Without loss of generality, suppose for some transaction with TX block $t$,
node $u$ decides \emph{valid} but node $v$ decides \emph{invalid}.
Then there exist a fragment $F' = \{ \dots, t', c'\}$ which $u$ received that contains a valid pair of $t$---$t'$.
There also exist a fragment $F'' = \{ \dots, t'', c''\}$ which $v$ received that does not contain or contains an invalid pair---$t''$.
In both cases, the $\textsf{get\_validity}(\cdot)$ function must have reached \Cref{line:valid-fragment}.
Due to \Cref{theorem:consensus}, we have $c' = c''$, otherwise the result would be \emph{unknown}.
Since $c' (= c'') = \langle \textsf{H}(t'), \dots \rangle$ we must have $\textsf{H}(t') = \textsf{H}(t'')$ and $t' \ne t''$ (because $t''$ is invalid).
In other words, the sender of $F''$ must be able to create some $t''$ that has the same digest as $t'$.
But this is only possible if the adversary can compute the inverse of $H(\cdot)$ with non-negligible probability.
Thus we have a contradiction and this completes the agreement proof.
Our protocol uses \Cref{alg:get-validity} which is also the validity definition,
this completes the validity proof.
\end{proof}

\Cref{theorem:validation-agreement} shows that agreement on CP blocks would lead to agreement on TX blocks when the nodes are running the validation protocol.
Just like in our prior work~\cite{implicitconsensus}, we call this behaviour implicit consensus.
One of the main advantages of our scheme over running a consensus algorithm on all the transactions is that 
the rate of transaction is no longer dependent on the consensus algorithm---ACS.
This enables horizontal scalability where adding new nodes would lead to higher global transaction rate.
In addition, a convenient consequence \Cref{theorem:validation-agreement} is unforgeability.
That is, no polynomial time adversary is able to create two chains $F = \{ \dots, t, c\}$ $F' = \{ \dots, t', c\}$ with correct hash pointers and the same end of chain $c$.
% Another way to think about it is if a transaction can be forged, then it cannot be agreed.

\subsection{Impossibility of liveness}
\Cref{theorem:validation-agreement} is a major result that allows significantly improved performance over traditional blockchain systems,
but it does not have all the properties of a typical Byzantine consensus protocol.
Now we show a negative result, where the liveness property of \Cref{def:validation} cannot be attained.
Meaning that trasanctions with adversaries cannot always be validated.

\begin{lemma}
There exist a valid transactions that cannot be validated eventually.
\end{lemma}
\begin{proof}
Suppose nodes $u$ and $v$ correctly perfomed the TX protocol which resulted a transaction.
Then when $u$ wants to validate it, it does so by sending \texttt{vd\_req} message to $v$.
$v$ can act maliciously and ignore all \texttt{vd\_req} message, then the transaction can never be validated.
\end{proof}
Although this is a negative result, it does not put the adversary in an advantageous position.
If the adversary is observed to ignore validation requests, then the honest nodes may prefer not to transact with her in the future.
Thus, to stay relevant in the system, the adversary need to comply to the protocol.

@@

\section{Performance analysis}
\label{sec:performance-analysis}
This section aims to analytically answer the scalability aspect of our research question.
That is, does the global throughput increase linearly with respect to the population size?
We begin by looking at the communication and time complexity of the consensus protocol,
and then the bandwidth requirement for a single transaction.
We build on top of those results to analyse the global throughput.

\subsection{Communication complexity of the consensus protocol}
\label{sec:cons-complexity}
The consensus protocol can bee seen as three parts,
so the communication complexity is the sum of these parts.
The first part is when every node sends their CP block to all the facilitators, which is $O(Nn)$ since there are $N$ nodes and $n$ facilitators.
Or simply $O(N)$ if we consider $n$ as a constant.

The second part is ACS.
The communication complexity of ACS is $O(n^2|v| + \lambda n^3 \log n)$~\cite{miller2016honey},
where $|v|$ is the size of largest message and $\lambda$ is the security parameter (described in \Cref{sec:model-assumptions}).
In our system, we wish to understand the scalability property.
Thus we consider the complexity as a function of $N$ rather than $n$ or $\lambda$.
Since $|v|$ is at most all the CP blocks from every node, we have $|v| = kN$,
where $k$ is a constant representing the size of one CP block.
Therefore the communication complexity of ACS in our system is $O(N)$.
Since we use a constant $n$, $O(N)$ communication complexity also holds for a single facilitator.

% TODO wrong?
The third and final part is the dissemination, where the facilitators broadcast the consensus result along with their signatures.
For the same reason as the first part, this is also $O(N)$.
Thus the combined communication complexity when $n$ is a constant is $O(N)$.

@@

\subsection{Duration of the consensus protocol}
\label{sec:cons-duration}
In order to make arguments on bandwidth or throughput in our purely asynchronous model, which are concepts that depend on time,
we must make some assumptions regarding our model to make arguments on the duration of the consensus protocol.
Note that it is not the same as the time complexity typically used in distributed systems.
In analysis of distributed systems, time complexity is often in terms of the number of rounds.
For example, ACS runs in a constant number of rounds because its subprotocols---reliable broadcast and binary Byzantine consensus---also run in a constant number of rounds~\cite{miller2016honey}.
However, in practice, making a unit of communication always has some overhead associated with it, for example serialising and writing it to some network socket.
Hence, for the remainder of our performance analysis, we add the following to our computational model.
For every unit of communication, we assume they take some non-negligible but constant time to perform.
Hence, from~\Cref{sec:cons-complexity} and the fact that the consensus protocol uses a constant number of rounds,
it follows that the consensus protocol has a duration of $O(N)$.

\subsection{Communication cost for transactions}
\label{sec:communication-cost-for-tx}
With the analysis on the duration of the consensus protocol,
we are ready to analyse the amount of data required to be transmitted over a link per transaction,
which we call the communication cost per transaction.
% First, we define bandwidth as the ``amount of data a link or network path can deliver per unit of
% time''~\cite{prasad2003bandwidth}.
To create and then validate a transaction,
the communication cost per transaction is of $O(l)$,
where $l$ is the length of the agreed fragment.
This can be seen from the fact that the largest message by far is the \texttt{vd\_resp} message,
which contains the agreed fragment.
The other messages (\texttt{tx\_req}, \texttt{tx\_resp} and \texttt{vd\_req}) are constant factors.
If we assume that every node performs transactions at a constant rate of $r_{\text{tx}}$ per second.
Then
$$l = r_{\text{tx}} D_{\text{c}},$$
where $D_{\text{c}}$ is the duration a round of the consensus protocol.
But from \Cref{sec:cons-duration},
we know that $D_{\text{c}}$ is of $O(N)$, thus the communication cost per transaction is $O(N)$.
This is intuitive because round duration would be longer if there are more CP blocks (more $N$), which means that the agreed fragments are longer (assuming nodes transact at a constant rate).
The behaviour is verified experimentally in \Cref{ch:implementation}.

\subsection{Linear global throughput}
\label{sec:global-throughput}
Using our results so far, we are able to analyse the global throughput.
First we clarify the bandwidth definition, which is ``the data rate at which a network link or a network path can transfer''~\cite{prasad2003bandwidth}.
Now, suppose every node has some fixed bandwidth $C$ per link, $N$ links and are making transactions at $r_{\text{tx}}$ per second.
Then we have the inequality
$$NC \ge r_{\text{tx}} l,$$
where $l$ is the length of the the agree fragment as before.
The inequality suggests that the rate for which transactions and validations are made cannot exceed the total bandwidth of all the links.

We note that the inequality does not hold if the node is only transacting with a subset of the population.
This is because it cannot use all the bandwidth available in all the links.
In the extreme case, if the node is only transacting with one other node, then it can only use the bandwidth of one link which is only $C$.
However, if that is the case, we can intelligently cache the \texttt{vd\_resp} messages as described in~\Cref{sec:caching}.
For this work, we analyse the worst case where every node transacts with a random node from the population,
and a new \texttt{vd\_resp} must be sent for every \texttt{vd\_req} message.

Consider the case where the system is making use of all the bandwidth, i.e. $NC = r_{\text{tx}} l$.
Recall that $l$ is of $O(N)$, that means LHS and RHS both grow linearly with respect to $N$.
Hence, there exist some constant $r_\text{tx}$ that makes use of all the available bandwidth regardless of $N$.
Finally, if every node in the network is transacting at a constant rate, then the global throughput (in terms of transactions per second) is linear w.r.t. the population size $N$.
If the system is not making use of all the bandwidth.
We also maintain a constant transaction rate by the same argument.
Thus a global throughput is also linear w.r.t. $N$.
We verify both of these claims experimentally in~\Cref{ch:implementation}.

@@

The problem can be formulated as follows.
Suppose an urn contains $N$ balls, $t$ are black (malicious) and $N-t$ are white (honest).
If $n$ balls are drawn uniformly at random without replacement,
what is the probability that more than $\lfloor \frac{n-1}{3} \rfloor$ are black?
The random variable $X$ in this case is the number of black balls, or the number of successful events.
It follows the hypergeometric distribution since we pick balls \emph{without} replacement~\cite{skala2013hypergeometric}.
Hence, we are interested in the following probability.
$$
1 - \sum_{k = 0}^{\lfloor \frac{n-1}{3} \rfloor} \Pr[X = k] = 
1 - \sum_{k = 0}^{\lfloor \frac{n-1}{3} \rfloor} \frac{ \binom{t}{k} \binom{N-t}{n-k} }{ \binom{N}{n} }
$$

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=1.0\textwidth]{hypergeometric}
  \caption{Plot of the probability of selecting more than $\lfloor \frac{n-1}{3} \rfloor$ black balls for
  different value of $t$ with $N$ fixed at 2000.}
  \label{fig:hypergeometric}
\end{figure}

On the other hand, due to the fact that hypergeometric distributions have light tails with ``faster-than-exponential fall-off''~\cite{skala2013hypergeometric},
the probability for picking more than $\lfloor \frac{n-1}{3} \rfloor$ black balls when 
the expected value is much smaller than $\lfloor \frac{n-1}{3} \rfloor$ is small.
We can use tail inequality to bound the probability of picking more than $\lfloor \frac{n-1}{3} \rfloor$ black balls when only $n\alpha$ are black where $0 \le \alpha \le \lfloor \frac{n-1}{3} \rfloor / n$.
The tail inequality is
$$
\Pr[X \ge E[X] + \tau n] \le e^{-2\tau^2n},
$$
where $E[X] = n\alpha$.
We are interested in $\Pr[X \ge \lfloor \frac{n-1}{3} \rfloor + 1]$, so
\begin{align*}
\tau &= \frac{\lfloor \frac{n-1}{3} \rfloor + 1}{n} - \alpha
\end{align*}
Putting $\tau$ back into the tail inequality we get the following bound.
$$
\Pr[X \ge \lfloor \frac{n-1}{3} \rfloor + 1] \le e^{-2 \big(\frac{\lfloor  \frac{n - 1}{3} \rfloor + 1}{n} - \alpha \big)^2 n}
$$
